### 2014-03-14 docs/paper.tex
Stuff on flash proxy.

Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing and
difficult to block.
Flash proxy's approach to unblockability is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
There exists a prototype transport that attempts to get both
obfuscation and address unblockability by combining flash proxy
with obfsproxy~\cite{obfs-flash}, however it is limited because it is not
possible to obfuscate flash proxy's outermost WebSocket layer.

>>>>

Flash proxy~\cite{flashproxy} attempts to address endpoint blocking by
conscripting web users as temporary proxies. Proxies last only as long as a web
user stays on a page, so the pool of proxies is constantly changing;
even if one of them is blocked, there will soon be another to replace it.
Flash proxy's approach to endpoint blocking is in a sense
the opposite of ours: where flash proxy uses cheap, disposable, individually blockable proxies,
we use just one high-value proxy, which shares its fate with network
infrastructure that is expensive to block.
Flash proxy itself does nothing to defend against content blocking.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on TCP,
but inside the WebSocket framing is the ordinary Tor protocol.
There exists a prototype transport that attempts to get both
content-based and endpoint-based blocking resistance by obfuscating traffic
with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
However it is limited because it is not
possible to obfuscate the outermost WebSocket layer;
the censor could decide simply to block all WebSocket.
